\section*{AD/A-1 Skyraider}

The Douglas AD Skyraider is a carrier-capable attack aircraft. Its development started during WWII, but it entered service with the USN in 1946. It was a large, single-engined propeller-driven aircraft. In 1962, it was redesignated as the A-1.

The Skyraider was initially armed with two 20 mm M3 cannon in the wings, but after experience in the early part of the Korean War this was increased to four in the AD-4 and subsequent versions. Later versions also had additional armor. It could also carry a heavy load on its centerline and underwing weapon stations.

In addition to the attack versions, it was adapted for radar search, anti-submarine, night attack, ECM, and night attack.

Early versions were a mainstay of the USN in the Korean War and later versions served in early part of the US involvement in the Vietnam War with the USN and USAF. It also saw limited service with the USMC. Most attack versions were single-seat, but the AD-5/A-1E had side-by-side seating for a pilot and copilot and was used by the USAF during Operation Farmgate with a USAF pilot and nominal South Vietnamese copilot. Attack versions were also used by RVAF, Armée de l'Air, and the air forces of Cambodia, Chad, and Gabon. The AD-4W radar-search version also served with the RN as the Skyraider AEW.1.

From 1967, USAF A-1s were equipped with the Stanley rocket extraction system. While not an ejection seat, this system used a rocket to pull the pilot our of the cockpit when bailing out.

A typical air-to-ground load in the Korean War might be 500~lb M64, 1000~lb M65, or 2000~lb M66 GP bombs or 750~lb BLU-1 napalm bombs on the centerline and inner wing pylons and HVAR rockets or 100~lb M30, 250~lb M57 bombs on the outer wing pylons.

A typical air-to-ground load in the Vietnam War might include 500~lb Mk~82 or 1000~lb Mk~83 GP bombs or 750~lb BLU-27 napalm bombs on the centerline and inner wing station, a single SUU-11 gunpod on an inner-wing station, and 100~lb M47 WP bombs, 250~lb Mk~81 GP bombs, 500~lb BLU-11 napalm bombs, LAU-3 or LAU-68 70 mm rocket pods, CBU-25 cluster bomb dispensers on the outer wing pylons.

ADCs are provided for:
\begin{itemize}
    \item AD-4
    \item AD-5 and A-1E
    \item AD-6 and A-1H
    \item AD-7 and A-1J
\end{itemize}