\section*{B-26 and A-26 Invader and Counter-Invader}

The Douglas B-26 Invader is a bomber and attack aircraft. It entered service in the USAAF before the end of WWII and saw combat in both the European and  Pacific Theaters. It later served with the USAF in the Korean War, during Operation Farm Gate in South Vietnam, and finally flying “Nimrod” interdiction missions over Laos. Many of its missions in Korea, Vietnam, and Laos were flown at night. It was also used by the Armée de l'air in the First Indochina War, the CIA in the Bay of Pigs Invasion, and in small number in many other conflicts in the 1950s and 1960s.

The B-26 was designed with two remote-control turrets, one dorsal and one ventral, similar to the rear turrets of the B-29 and each equipped with two .50 cal M2 machine guns. The turrets were operated by a single gunner, positioned behind the bomb bay, who monitored the sky though large ventral and dorsal windows and aimed both turrets with an periscope sight. The lower turret was removed in many aircraft to give more fuel capacity. In later service, both turrets were removed as defensive guns were not useful for its missions in Vietnam and Laos. 

The B-26 also had a number of different noses, with the most common being the solid nose with eight .50 cal M2 machine guns on the B-26B and the gunless glass nose (which allowed the use of a bombsight) on the B-26C. There was also some variation in guns fitted in the wings.

The B-26K was a rebuilt version, necessary after several earlier aircraft had been lost because of metal fatigue in the main wing spar. It saw combat from 1966 to 1969 with the USAF, flying from Thailand on night-time interdiction missions in Laos. 

The Invader was originally designated A-26. In 1948, it was redesignated B-26, reusing the designation of the earlier B-26 Marauder which by then had left service. In 1966, the B-26K was redesignated A-26A to avoid the perception of a bomber being based in supposedly neutral Thailand.

Typical armament in the Korean War, beyond the guns, was 500 or 1000 lb bombs in the bomb bay and 500 or 1000 lb bombs, 110 gal napalm cans, or HVARs or parachute flares on the wing stations.

Typical armament of Farm Gate B-26s was TODO.

Typical armament of Nimrod B-26Ks was fragmentation and incendiary bombs in the bomb bay, and then a mixture of illumination pods, napalm, LAU-3A rocket pods, and CBUs under the wings.

ADCs are provided for the:
\begin{itemize}
\item B-26B (Two Turrets)
\item B-26B (One Turret)
\item B-26B (No Turrets)
\item B-26C (Two Turrets)
\item B-26C (One Turret)
\item B-26C (No Turrets)
\item B-26K
\item A-26A
\end{itemize}
