\section*{Yak-9}

The Yakovlev Yak-9 is a propeller-driven fighter that was developed during WWII and which first entered service with the Soviet Union in 1942. After WWII, it was supplied to many Soviet allies. The NATO reporting name is “Frank.”

There are several versions. The Yak-9D is a long-ranged escort fighter and is armed with one 20 mm ShVAK cannon and one 12.7 mm UBS machine gun. The Yak-9U has a more powerful engine, more use of aluminium, and gains a second UBS machine gun. The Yak-9P is a development of the -9U with completely metal wings.

The Yak-9U/-9P were used by the North Korean KPAF and saw extensive service in the first weeks of the Korean War. They were also used by the Chinese PLAAF.

ADCs are provided for:
\begin{itemize}
\item Yak-9D
\item Yak-9U
\item Yak-9P
\end{itemize}

\section*{Iluyshin Il-10}

The Ilyushin Il-10 is a propeller-driven ground-attack aircraft developed during WWII as a replacement for the famous Il-2 Sturmovik. It entered service with the Soviet Union in 1944. After the war, it was supplied to many Soviet allies and was also manufactured under license in Czechoslovakia.

Like its predecessor, the Il-10 features extensive armor for the crew and engine and a ventral defensive gun to protect from attacks from the rear. The initial Il-10 has two 23 mm VYa-23 cannons and two 7.62 mm ShKAS machine guns in the wings, with 150 and 750 rounds each, respectively, plus a 12.7 mm UBT machine gun with 150 rounds protecting the tail. Later versions have four 23 mm NR-23 cannons in the wings and a 20 mm B-20 cannon in the ventral mount.

A typical weapon load would be four 100 kg bombs, two in the bomb bays and two on the wing stations, or two 250 kg bombs on the wings. Alternatively, the wing stations could carry a total of eight RS-82 or four RS-132 rockets.

The Il-10 was used by the North Korean KPAF and saw extensive service in the first weeks of the Korean War, before suffering large losses against USAF fighters. They were also used by the Chinese PLAAF.

ADCs are provided for:
\begin{itemize}
\item Il-10
\end{itemize}
