\section*{Meteor}

The Gloster Meteor was the first British jet fighter and the only Allied jet to see combat in WW2. It entered service as a day fighter with the RAF in 1944 and continued to serve in various roles after the war. It was powered by two wing-mounted centrifugal flow jet engines, had unswept wings, and was armed with four 20 mm guns.

The F.8 was a post-WW2 development. Compared to its immediate predecessor, the late-WW2 F.4, it had more powerful Rolls-Royce Derwent 8 engines, a lengthened fuselage, and a new tail to solve center-of-gravity problems, improved visibility from the cockpit, and the capability to carry air-to-ground weapons. In common with many early jet fighters, it suffered from shorter ranges, and this was addressed by equipping it with a jettisonable, conformal ventral fuel tank. It was introduced into RAF service in 1949. In the 1950s, the unsophisticated aerodynamics of the Meteor led it to be outclassed by newer swept-wing fighters like the MiG-15 and F-86, and so the F.8 was the last fighter version produced. Subsequent versions were reconnaissance and night fighter.
 
The FR.9 was a photoreconnaissance version of the F.8. It had an extended nose for a single camera that could be configured on the ground to be either overhead or oblique and retained the full combat capability of the F.8. It was introduced into RAF service in 1950.

The F.8 served as the main RAF fighter and fighter-bomber in the 1950s. It was also extensively used by No.~77 Squadron RAAF in the Korean War, replacing their F-51Ds in April 1951. In the Suez crisis, the F.8 was used by the Egyptian, Syrian, and Israeli air forces, and the FR.9 by the RAF. The F.8 or FR.9 also served in the air forces of Belgium, Brazil, Denmark, Ecuador, and the Netherlands. The Meteor was replaced in RAF service by the Canadair Sabre 4, Hawker Hunter, and Gloster Javelin and in RAAF service by the CAC Sabre.

% Sabre 4 in RAF?
% Other users?
% Add PR.10?

A typical air-to-air load would be the ventral 175 gal fuel tank, perhaps with two 100 gal fuel tanks on the wings to increase patrol time. For air-to-ground, the Meteor could carry two 1000 lb bombs or eight or sixteen RP-3 rockets in addition to the ventral tank.

ADCs are provided for the:
\begin{itemize}
\item Meteor F.8
\item Meteor FR.9
\end{itemize}
